### 2022-08-23 acronyms/acronyms.tex
update acronym

%%%%% put this in right before draft
%%%%% acronyms
% alphabetical ordering is automated
\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
\newacronym{anl}{ANL}{Argonne National Laboratory}
\newacronym{inl}{INL}{Idaho National Laboratory}
\newacronym{npp}{NPP}{Nuclear Power Plant}
\newacronym{nrs}{NHRES}{Nuclear Renewable Hybrid Energy System}
\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
\newacronym{smr}{SMR}{Small Modular Reactor}
\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
\newacronym{nus}{NuScale}{NuScale Power, LLC}
\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
\newacronym{epri}{EPRI}{Electric Power Research Institute}
\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
\newacronym{ci}{CI}{Consistency Index}
\newacronym{cr}{CR}{Consistency Ratio}
\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
\newacronym{lwr}{LWR}{Light Water Reactor}
\newacronym{aps}{APS}{Arizona Public Service} 
\newacronym{arm}{ARMA}{Autoregressive Moving Average} 
\newacronym{eia}{EIA}{Energy Information Agency}
\newacronym{epa}{EPA}{Environmental Protection Agency}
\newacronym{hx}{HX}{Heat exchanger} 
\newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
\newacronym{mwe}{MWe}{Megawatts electricity}
\newacronym{mwt}{MWth}{Megawatts thermal energy}
\newacronym{ies}{IES}{Integrated Energy System} 
\newacronym{pv}{PV}{Palo Verde Generating Station} 
\newacronym{rav}{RAVEN}{Risk Analysis Virtual Environment} 
\newacronym{ro}{RO}{Reverse Osmosis} 
\newacronym{rom}{ROM}{Reduced Order Model} 
\newacronym{spe}{SPECO}{Specific Exergy Costing} 
\newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
\newacronym{ieo}{IESO}{Independent Electricity System Operator}
\newacronym{us}{US}{United States}
\newacronym{med}{MED}{Multiple-Effect Distillation}
\newacronym{ed}{ED/EDR}{Electrodialysis Reversal}
\newacronym{nf}{NF}{Nanofiltration}
\newacronym{jls}{J}{Joules}
\newacronym{nre}{NREI}{Nuclear Renewable Energy Integration}
\newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
\newacronym{iso}{ISO}{Independent System Operator} 
\newacronym{msf}{MSF}{Multi-Stage Flash} 
\newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
\newacronym{un}{UN}{United Nations}
\newacronym{ict}{ICT}{Information and communications technologies}
\newacronym{nws}{NWS}{Nuclear Weapons States}
\newacronym{nnws}{NNWS}{Non Nuclear Weapons States}
\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
\newacronym{snm}{SNM}{Special Nuclear Material}
\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
\newacronym{nnsa}{NNSA}{National Nuclear Security Administration}
\newacronym{fbi}{FBI}{Federal Bureau of Investigation}
\newacronym{nsg}{NSG}{Nuclear Suppliers Group}
\newacronym{mad}{MAD}{Mutually Assured Destruction}
\newacronym{wmd}{WMD}{Weapons of Mass Destruction}
\newacronym{sq}{SQ}{Significant Quantity}
\newacronym{der}{DER}{Distributed Energy Resource}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
\newacronym{usa}{US}{United States}
\newacronym{doe}{DOE}{United States Department of Energy}
\newacronym{pfc}{PFC}{Primary Frequency Control}
\newacronym{sfc}{SFC}{Secondary Frequency Control}
\newacronym{ace}{ACE}{Area Control Error}
\newacronym{var}{VAr}{Volt-Amps Reactive}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{nyi}{NYISO}{New York Independent System Operator}
\newacronym{ac}{AC}{Alternating Current}
\newacronym{dc}{DC}{Direct Current}
\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
\newacronym{inc}{I\&C}{Instrumentation and Controls}
%%%%%

>>>>

%%%%% put this in right before draft
%%%%% acronyms
% alphabetical ordering is automated
\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
\newacronym{anl}{ANL}{Argonne National Laboratory}
\newacronym{bol}{BOL}{beginning-of-life}
\newacronym{cae}{CAES}{Center for Advanced Energy Studies}
\newacronym{ccc}{CCC}{Computing Community Consortium}
\newacronym{ci}{CI}{Consistency Index}
\newacronym{cps}{CPS}{Cyber-Physical Systems}
\newacronym{cr}{CR}{Consistency Ratio}
\newacronym{cs}{CS}{Critical System}
\newacronym{doe}{DOE}{United States Department of Energy}
\newacronym{dnp}{DNP3}{Distributed Network Protocol 3}
\newacronym{dos}{DDoS}{Distributed Denial of Service}
\newacronym{eia}{EIA}{U.S. Energy Information Administration}
\newacronym{eol}{EOL}{end-of-life}
\newacronym{epri}{EPRI}{Electric Power Research Institute}
\newacronym{hmi}{HMI}{Human Machine Interface}
\newacronym{hsl}{HSSL}{Human System Simulation Laboratory}
\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
\newacronym{ic}{I\&C}{Instrumentation \& Controls}
\newacronym{ics}{ICS}{Industrial Control Systems}
\newacronym{ies}{IES}{Integrated Energy System}
\newacronym{imu}{IMUNES}{Integrated Multiprotocol Network Emulator/Simulator}
\newacronym{inl}{INL}{Idaho National Laboratory}
\newacronym{ip}{IP}{Internet Protocol}
\newacronym{jcp}{JCPOA}{Joint Comprehensive Plan of Action}
\newacronym{khp}{KHNP}{Korean Hydro \& Nuclear Power Co., Ltd}
\newacronym{kmp}{KMP}{key measurement point}
\newacronym{lms}{LMS}{Learning Management System}
\newacronym{loc}{LOCA}{Loss of Coolant Accident}
\newacronym{mim}{MITM}{Man in the Middle}
\newacronym{mol}{MOL}{middle-of-life}
\newacronym{mwe}{MWe}{Megawatts-electric}
\newacronym{nei}{NEI}{Nuclear Energy Institute}
\newacronym{nerc}{NERC}{North American Electric Reliability Corporation}
\newacronym{neu}{NEUP}{Nuclear Energy University Program}
\newacronym{nit}{NITRD}{Networking Information Technology Research \& Development Program}
\newacronym{npp}{NPP}{Nuclear Power Plant}
\newacronym{nsf}{NSF}{National Science Foundation}
\newacronym{nus}{NuScale}{NuScale Power, LLC}
\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
\newacronym{oer}{OER}{Online Educational Resource}
\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
\newacronym{pha}{PHA}{Preliminary Hazards Analysis}
\newacronym{plc}{PLC}{Programmable Logic Controller}
\newacronym{pra}{PRA}{Probabilistic Risk Assessment}
\newacronym{pwr}{PWR}{Pressurized Water Reactor}
\newacronym{roi}{ROI}{Return on Investment}
\newacronym{sca}{SCADA}{Supervisory Control and Data Acquisition}
\newacronym{smr}{SMR}{Small Modular Reactor}
\newacronym{snm}{SNM}{special nuclear material}
\newacronym{tcp}{TCP/IP}{Transmission Control Protocol/Internet Protocol}
\newacronym{tva}{TVA}{Tennessee Valley Authority}
\newacronym{udp}{UDP}{User Datagram Protocol}
\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
\newacronym{vfd}{VFD}{Variable Frequency Drive}
\newacronym{wsc}{WSC}{Western Services Corporation}
\newacronym{mba}{MBA}{material balance area}
\newacronym{nma}{NMA}{nuclear materials accounting}
\newacronym{sei}{SEID}{standard error of the inventory difference}
\newacronym{tru}{TRU}{transuranic element}
\newacronym{des}{DES}{discrete event simulation}
\newacronym{sq}{SQ}{significant quantity}
\newacronym{pyn}{PyNE}{Python for Nuclear Engineering}
\newacronym{haz}{HAZOP}{hazard and operability analysis}
\newacronym{msr}{MSR}{molten salt reactor}
\newacronym{mpt}{MPACT}{Materials Protection, Accounting and Control Technology}
\newacronym{aoo}{AOO}{Anticipated Operational Occurrences}
\newacronym{dbe}{DBE}{Design Basis Events}
\newacronym{bde}{BDBE}{Beyond Design Basis Events}
\newacronym{ies}{IES}{Integrated Energy Systems}
\newacronym{mca}{MC\&A}{Materials Control and Accountability}
\newacronym{ahp}{AHP}{Analytical Hierarchy Process}
\newacronym{anl}{ANL}{Argonne National Laboratory}
\newacronym{inl}{INL}{Idaho National Laboratory}
\newacronym{npp}{NPP}{Nuclear Power Plant}
\newacronym{nrs}{NHRES}{Nuclear Renewable Hybrid Energy System}
\newacronym{orl}{ORNL}{Oak Ridge National Laboratory}
\newacronym{smr}{SMR}{Small Modular Reactor}
\newacronym{ump}{UAMPS}{Utah Associated Municipal Power Systems}
\newacronym{nus}{NuScale}{NuScale Power, LLC}
\newacronym{nrc}{NRC}{United States Nuclear Regulatory Commission}
\newacronym{epri}{EPRI}{Electric Power Research Institute}
\newacronym{htse}{HTSE}{High Temperature Steam Electrolysis}
\newacronym{lwr}{LWR}{Light Water Reactor}
\newacronym{aps}{APS}{Arizona Public Service} 
\newacronym{arm}{ARMA}{Autoregressive Moving Average} 
\newacronym{eia}{EIA}{Energy Information Agency}
\newacronym{epa}{EPA}{Environmental Protection Agency}
\newacronym{hx}{HX}{Heat exchanger} 
\newacronym{msf}{MSF}{Multi-Stage Flash Distillation} 
\newacronym{mwt}{MWth}{Megawatts thermal energy}
\newacronym{ies}{IES}{Integrated Energy System} 
\newacronym{pv}{PV}{Palo Verde Generating Station} 
\newacronym{rav}{RAVEN}{Risk Analysis Virtual Environment} 
\newacronym{ro}{RO}{Reverse Osmosis} 
\newacronym{rom}{ROM}{Reduced Order Model} 
\newacronym{spe}{SPECO}{Specific Exergy Costing} 
\newacronym{ufs}{U-FSAR}{Updated Final Safety Analysis Report} 
\newacronym{ieo}{IESO}{Independent Electricity System Operator}
\newacronym{med}{MED}{Multiple-Effect Distillation}
\newacronym{ed}{ED/EDR}{Electrodialysis Reversal}
\newacronym{nf}{NF}{Nanofiltration}
\newacronym{jls}{J}{Joules}
\newacronym{nre}{NREI}{Nuclear Renewable Energy Integration}
\newacronym{nrt}{NRTL}{Aspen Electrolyte Non-Random Two-Liquid}
\newacronym{ide}{IDE}{Israel Desalination Enterprises} 
\newacronym{iso}{ISO}{Independent System Operator} 
\newacronym{npt}{NPT}{Treaty on the Non-Proliferation of Nuclear Weapons}
\newacronym{un}{UN}{United Nations}
\newacronym{ict}{ICT}{Information and communications technologies}
\newacronym{nws}{NWS}{Nuclear Weapons States}
\newacronym{nnws}{NNWS}{Non Nuclear Weapons States}
\newacronym{iaea}{IAEA}{International Atomic Energy Agency}
\newacronym{nnsa}{NNSA}{National Nuclear Security Administration}
\newacronym{fbi}{FBI}{Federal Bureau of Investigation}
\newacronym{nsg}{NSG}{Nuclear Suppliers Group}
\newacronym{mad}{MAD}{Mutually Assured Destruction}
\newacronym{wmd}{WMD}{Weapons of Mass Destruction}
\newacronym{sq}{SQ}{Significant Quantity}
\newacronym{der}{DER}{Distributed Energy Resource}
\newacronym{ferc}{FERC}{Federal Energy Regulatory Commission}
\newacronym{usa}{US}{United States}
\newacronym{pfc}{PFC}{Primary Frequency Control}
\newacronym{sfc}{SFC}{Secondary Frequency Control}
\newacronym{ace}{ACE}{Area Control Error}
\newacronym{var}{VAr}{Volt-Amps Reactive}
\newacronym{dsm}{DSM}{Demand Side Management}
\newacronym{nyi}{NYISO}{New York Independent System Operator}
\newacronym{ac}{AC}{Alternating Current}
\newacronym{dc}{DC}{Direct Current}
%%%%%
